---
title: "plot Campbell"
author: "Fonti"
date: "23/01/2021"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## LÖTSCHENTAL Campbell site by syte

This is report to check the status of Ltal raw data. The report is from: 

```{r}
Sys.time()
```

```{r, include=FALSE}
# This script of for making dyGraph

library(tidyverse)
library(dygraphs)
library(xts)


# Load data
source('1.Import_FTP_data.R')
head(DATA)


```

## Plots Dendrometer N08

```{r dendro_N08, echo=FALSE}
  SITE <- DATA[grep("N08",names(DATA))] %>%as.data.frame(col.names = "") %>%
  mutate_at(grep("Avg",colnames(.)),funs(as.character)) %>%
  mutate_at(grep("Avg",colnames(.)),funs(as.numeric)) %>%
  mutate(TIMESTAMP = as.POSIXct(TIMESTAMP)) %>%
  filter(TIMESTAMP > as.POSIXct('2020-01-01') & TIMESTAMP < as.POSIXct('2021-12-31'))

  SITE %>%
  select(starts_with("Dendr")) %>%
  xts(SITE[,-1:-2], order.by=SITE[,1]) %>%
  dygraph(main = "N08") %>% dyRangeSelector(height=50) %>%
  dyOptions(fillGraph = FALSE) 
```

## Plots Sapflow N08

```{r sap_N08, echo=FALSE}
  SITE <- DATA[grep("N08",names(DATA))] %>%as.data.frame(col.names = "") %>%
  mutate_at(grep("Avg",colnames(.)),funs(as.character)) %>%
  mutate_at(grep("Avg",colnames(.)),funs(as.numeric)) %>%
  mutate(TIMESTAMP = as.POSIXct(TIMESTAMP)) %>%
  filter(TIMESTAMP > as.POSIXct('2020-01-01') & TIMESTAMP < as.POSIXct('2021-12-31'))

  SITE %>%
  select(starts_with("Granier")) %>%
  xts(SITE[,-1:2], order.by=SITE[,1]) %>%
  dygraph(main = "N08") %>% dyRangeSelector(height=50) %>%
  dyOptions(fillGraph = TRUE) 
```

## Plots Dendrometer N13Da

```{r dendro_N13Da, echo=FALSE}
  SITE <- DATA[grep("N13Da",names(DATA))] %>%as.data.frame(col.names = "") %>%
  mutate_at(grep("Avg",colnames(.)),funs(as.character)) %>%
  mutate_at(grep("Avg",colnames(.)),funs(as.numeric)) %>%
  mutate(TIMESTAMP = as.POSIXct(TIMESTAMP)) %>%
  filter(TIMESTAMP > as.POSIXct('2020-01-01') & TIMESTAMP < as.POSIXct('2021-12-31'))

  SITE %>%
  select(starts_with("Dendr")) %>%
  xts(SITE[,-1:-2], order.by=SITE[,1]) %>%
  dygraph(main = "N13Da") %>% dyRangeSelector(height=50) %>%
  dyOptions(fillGraph = FALSE) 
```

## Plots Sapflow N13Da

```{r sap_N13Da, echo=FALSE}
  SITE <- DATA[grep("N13Da",names(DATA))] %>%as.data.frame(col.names = "") %>%
  mutate_at(grep("Avg",colnames(.)),funs(as.character)) %>%
  mutate_at(grep("Avg",colnames(.)),funs(as.numeric)) %>%
  mutate(TIMESTAMP = as.POSIXct(TIMESTAMP)) %>%
  filter(TIMESTAMP > as.POSIXct('2020-01-01') & TIMESTAMP < as.POSIXct('2021-12-31'))

  SITE %>%
  select(starts_with("Granier")) %>%
  xts(SITE[,-1:2], order.by=SITE[,1]) %>%
  dygraph(main = "N13Da") %>% dyRangeSelector(height=50) %>%
  dyOptions(fillGraph = TRUE) 
```

  
## Plots Dendrometer N13Db

```{r dendro_N13Db, echo=FALSE}
  SITE <- DATA[grep("N13Db",names(DATA))] %>%as.data.frame(col.names = "") %>%
  mutate_at(grep("Avg",colnames(.)),funs(as.character)) %>%
  mutate_at(grep("Avg",colnames(.)),funs(as.numeric)) %>%
  mutate(TIMESTAMP = as.POSIXct(TIMESTAMP)) %>%
  filter(TIMESTAMP > as.POSIXct('2020-01-01') & TIMESTAMP < as.POSIXct('2021-12-31'))

  SITE %>%
  select(starts_with("Dendr")) %>%
  xts(SITE[,-1:-2], order.by=SITE[,1]) %>%
  dygraph(main = "N13Db") %>% dyRangeSelector(height=50) %>%
  dyOptions(fillGraph = FALSE) 
```

## Plots Sapflow N13Db

```{r sap_N13Db, echo=FALSE}
  SITE <- DATA[grep("N13Db",names(DATA))] %>%as.data.frame(col.names = "") %>%
  mutate_at(grep("Avg",colnames(.)),funs(as.character)) %>%
  mutate_at(grep("Avg",colnames(.)),funs(as.numeric)) %>%
  mutate(TIMESTAMP = as.POSIXct(TIMESTAMP)) %>%
  filter(TIMESTAMP > as.POSIXct('2020-01-01') & TIMESTAMP < as.POSIXct('2021-12-31'))

  SITE %>%
  select(starts_with("Granier")) %>%
  xts(SITE[,-1:2], order.by=SITE[,1]) %>%
  dygraph(main = "N13Db") %>% dyRangeSelector(height=50) %>%
  dyOptions(fillGraph = TRUE) 
```

  
## Plots Dendrometer S16a

```{r dendro_N16a, echo=FALSE}
  SITE <- DATA[grep("S16a",names(DATA))] %>%as.data.frame(col.names = "") %>%
  mutate_at(grep("Avg",colnames(.)),funs(as.character)) %>%
  mutate_at(grep("Avg",colnames(.)),funs(as.numeric)) %>%
  mutate(TIMESTAMP = as.POSIXct(TIMESTAMP)) %>%
  filter(TIMESTAMP > as.POSIXct('2020-01-01') & TIMESTAMP < as.POSIXct('2021-12-31'))

  SITE %>%
  select(starts_with("Dendr")) %>%
  xts(SITE[,-1:-2], order.by=SITE[,1]) %>%
  dygraph(main = "S16a") %>% dyRangeSelector(height=50) %>%
  dyOptions(fillGraph = FALSE) 
```

## Plots Sapflow S16a

```{r sap_N16a, echo=FALSE}
  SITE <- DATA[grep("S16a",names(DATA))] %>%as.data.frame(col.names = "") %>%
  mutate_at(grep("Avg",colnames(.)),funs(as.character)) %>%
  mutate_at(grep("Avg",colnames(.)),funs(as.numeric)) %>%
  mutate(TIMESTAMP = as.POSIXct(TIMESTAMP)) %>%
  filter(TIMESTAMP > as.POSIXct('2020-01-01') & TIMESTAMP < as.POSIXct('2021-12-31'))

  SITE %>%
  select(starts_with("Granier")) %>%
  xts(SITE[,-1:2], order.by=SITE[,1]) %>%
  dygraph(main = "S16a") %>% dyRangeSelector(height=50) %>%
  dyOptions(fillGraph = TRUE) 
```

  
## Plots Dendrometer S16b

```{r dendro_N16b, echo=FALSE}
  SITE <- DATA[grep("S16b",names(DATA))] %>%as.data.frame(col.names = "") %>%
  mutate_at(grep("Avg",colnames(.)),funs(as.character)) %>%
  mutate_at(grep("Avg",colnames(.)),funs(as.numeric)) %>%
  mutate(TIMESTAMP = as.POSIXct(TIMESTAMP)) %>%
  filter(TIMESTAMP > as.POSIXct('2020-01-01') & TIMESTAMP < as.POSIXct('2021-12-31'))

  SITE %>%
  select(starts_with("Dendr")) %>%
  xts(SITE[,-1:-2], order.by=SITE[,1]) %>%
  dygraph(main = "S16b") %>% dyRangeSelector(height=50) %>%
  dyOptions(fillGraph = FALSE) 
```

## Plots Sapflow S16b

```{r sap_N16b, echo=FALSE}
  SITE <- DATA[grep("S16b",names(DATA))] %>%as.data.frame(col.names = "") %>%
  mutate_at(grep("Avg",colnames(.)),funs(as.character)) %>%
  mutate_at(grep("Avg",colnames(.)),funs(as.numeric)) %>%
  mutate(TIMESTAMP = as.POSIXct(TIMESTAMP)) %>%
  filter(TIMESTAMP > as.POSIXct('2020-01-01') & TIMESTAMP < as.POSIXct('2021-12-31'))

  SITE %>%
  select(starts_with("Granier")) %>%
  xts(SITE[,-1:2], order.by=SITE[,1]) %>%
  dygraph(main = "S16b") %>% dyRangeSelector(height=50) %>%
  dyOptions(fillGraph = TRUE) 
```

  
## Plots Dendrometer S19

```{r dendro_S19, echo=FALSE}
  SITE <- DATA[grep("S19",names(DATA))] %>%as.data.frame(col.names = "") %>%
  mutate_at(grep("Avg",colnames(.)),funs(as.character)) %>%
  mutate_at(grep("Avg",colnames(.)),funs(as.numeric)) %>%
  mutate(TIMESTAMP = as.POSIXct(TIMESTAMP)) %>%
  filter(TIMESTAMP > as.POSIXct('2020-01-01') & TIMESTAMP < as.POSIXct('2021-12-31'))

  SITE %>%
  select(starts_with("Dendr")) %>%
  xts(SITE[,-1:-2], order.by=SITE[,1]) %>%
  dygraph(main = "S19") %>% dyRangeSelector(height=50) %>%
  dyOptions(fillGraph = FALSE) 
```

## Plots Sapflow S19

```{r sap_S19, echo=FALSE}
  SITE <- DATA[grep("S19",names(DATA))] %>%as.data.frame(col.names = "") %>%
  mutate_at(grep("Avg",colnames(.)),funs(as.character)) %>%
  mutate_at(grep("Avg",colnames(.)),funs(as.numeric)) %>%
  mutate(TIMESTAMP = as.POSIXct(TIMESTAMP)) %>%
  filter(TIMESTAMP > as.POSIXct('2020-01-01') & TIMESTAMP < as.POSIXct('2021-12-31'))

  SITE %>%
  select(starts_with("Granier")) %>%
  xts(SITE[,-1:2], order.by=SITE[,1]) %>%
  dygraph(main = "S19") %>% dyRangeSelector(height=50) %>%
  dyOptions(fillGraph = TRUE) 
```

  
## Plots Dendrometer S22

```{r dendro_S22, echo=FALSE}
  SITE <- DATA[grep("S22",names(DATA))] %>%as.data.frame(col.names = "") %>%
  mutate_at(grep("Avg",colnames(.)),funs(as.character)) %>%
  mutate_at(grep("Avg",colnames(.)),funs(as.numeric)) %>%
  mutate(TIMESTAMP = as.POSIXct(TIMESTAMP)) %>%
  filter(TIMESTAMP > as.POSIXct('2020-01-01') & TIMESTAMP < as.POSIXct('2021-12-31'))

  SITE %>%
  select(starts_with("Dendr")) %>%
  xts(SITE[,-1:-2], order.by=SITE[,1]) %>%
  dygraph(main = "S22") %>% dyRangeSelector(height=50) %>%
  dyOptions(fillGraph = FALSE) 
```

## Plots Sapflow S22

```{r sap_S22, echo=FALSE}
  SITE <- DATA[grep("S22",names(DATA))] %>%as.data.frame(col.names = "") %>%
  mutate_at(grep("Avg",colnames(.)),funs(as.character)) %>%
  mutate_at(grep("Avg",colnames(.)),funs(as.numeric)) %>%
  mutate(TIMESTAMP = as.POSIXct(TIMESTAMP)) %>%
  filter(TIMESTAMP > as.POSIXct('2020-01-01') & TIMESTAMP < as.POSIXct('2021-12-31'))

  SITE %>%
  select(starts_with("Granier")) %>%
  xts(SITE[,-1:2], order.by=SITE[,1]) %>%
  dygraph(main = "S22") %>% dyRangeSelector(height=50) %>%
  dyOptions(fillGraph = TRUE) 
```

  